### 2014-09-23 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to numerical mesh section

For the simulation, a measure of how well the flow field is resolved can be estimated by using the non-dimensional expression $D^*/\dx$. Here, $D^*$ is the characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
\begin{equation}
D^* = \left(
     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g}}
     \right)^\frac{2}{5} 
\label{eq:mesh}
\end{equation}
From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the relation $Q^* = (D^*/D)^{5/2}$. Here, $D$ is the physical diameter of the base of the fire specified in the simulation. Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 18.8 for the initial couch fire (peak HRR of 5.4~MW) and 28.3 for the basement flashover fire (HRR of 15~MW). Based on validation work performed for the U.S. Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were adequate for engineering calculations. The grid resolution used in this model is within or exceeds typical engineering $D^*/\dx$ values.

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Rear}
\caption{Front (left) and rear (right) of the structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}

>>>>

For the simulation, a measure of how well the flow field is resolved can be estimated by using the non-dimensional expression $D^*/\dx$. Here, $D^*$ is the characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
\begin{equation}
D^* = \left(
     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g}}
     \right)^\frac{2}{5} 
\label{eq:mesh}
\end{equation}
From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the relation $Q^* = (D^*/D)^{5/2}$. Here, $D$ is the physical diameter of the base of the fire specified in the simulation. Based on validation work performed for the U.S. Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were adequate for engineering calculations. Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the ratio of the characteristic fire diameter to cell size ($D^*/\dx$) was 18 for the initial couch fire (combined HRR of 5~MW), 31 for the secondary flashover fire in the basement (combined HRR of 19~MW), and 32 for the maximum prescribed fire size in the structure (combined HRR of 20~MW). Therefore, the grid resolution used in this model results in a $D^*/\dx$ ratio that exceeds typical engineering values.

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
\caption{Front (left) and rear (right) of the structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}
